\huge Modeling Intervention Strategies for United States TB Control

### 2013-07-28 in_progress/presentations/poster/reuMHC2013.tex
some little changes; about to start working on a cost source breakdown graph for the base system

\begin{frame}
  \begin{columns}
    \begin{column}{.3\textwidth}
      \vspace{-3em}
      \begin{block}{Introduction}
        Epidemiological models offer insight into the structure of disease
        outbreaks and the merits of various interventions. The most common
        epidemiological models are compartmental differential equation models,
        such as the SIR system, illustrated in figures~\ref{fig:SIRFlowchart}
        and~\ref{eq:SIRdes}. 
       %TODO equalize figure heights
        \begin{block}{}
          \begin{column}{.39\textwidth}
            \begin{figure}[h]
              \begin{center}
                \begin{tikzpicture}
                  \node [compartment] (S) {Susceptible (S)};
                  \node [compartment, below of=S] (I) {Infected (I)};
                  \node [compartment, below of=I] (R) {Recovered (R)};
                  \path [line] (S) -- node [compartment rate] {$\beta S(t)I(t)$} (I);
                  \path [line] (I) -- node [compartment rate] {$\gamma I(t)$} (R);
                \end{tikzpicture}
              \end{center}
              \caption{This flowchart depicts the standard SIR epidemiological
                       model. It is accomponanied by the system of differential
                       equations~\ref{eq:SIRdes}.}
              \label{fig:SIRFlowchart}
            \end{figure}
          \end{column}
          \begin{column}{.39\textwidth}
            \begin{figure}[h]
              \begin{align*}
                \frac{dS}{dt} &= -\beta S(t)I(t) \\
                \frac{dI}{dt} &= \beta S(t)I(t) - \gamma I(t) \\
                \frac{dR}{dt} &= \gamma I(t)\\
                N             &= S(t) + I(t) + R(t)\\
              \end{align*}
              \caption{The system of differential equations governing the SIR
                       model.}
              \label{eq:SIRdes}
            \end{figure}
          \end{column}
        \end{block}
      \end{block}

@@

@@

        \begin{enumerate}

@@

        \end{enumerate}

@@

            \begin{enumerate}
              \item Active TB: \$14,014.90
              \item LTBI: \$403.45
            \end{enumerate}

@@

@@

        We also wrote a stochastic agent-based version of the Hill model in both
        NetLogo and C++.

@@

      \begin{block}{Stochastic Models as a Measure of Variability}
        The stochastic model gives us a sense of the variability of the results
        of the deterministic model.
        \begin{block}{}
          \begin{column}{.45\textwidth}
            \begin{figure}[h]
              \begin{center}
                \includegraphics[width=\textwidth]{IN0dist}
              \end{center}
              \caption{Distribution of USB Incidence (C++) with fitted Normal curve}
              \label{fig:IN0dist}
            \end{figure}
          \end{column}
          \begin{column}{.45\textwidth}
            \begin{figure}[h]
              \begin{center}
                \includegraphics[width=\textwidth]{IN1dist}
              \end{center}
              \caption{Distribution of FB Incidence (C++) with fitted Normal curve}
              \label{fig:IN1dist}
            \end{figure}
          \end{column}
        \end{block}
      \end{block}

      \begin{block}{Future Extensions}
        Possible extensions to our model include the incorporation of non-homogeneous
        contact structures and MDR (multi-drug resistant) TB.
      \end{block}

>>>>

\begin{frame}
  \begin{columns}
    \begin{column}{.3\textwidth}
      \vspace{-3.6em}
      \begin{block}{Introduction}
        Epidemiological models offer insight into the structure of disease
        outbreaks and the merits of various interventions. The most common
        epidemiological models are compartmental differential equation models,
        such as the SIR system, illustrated in figures~\ref{fig:SIRFlowchart}
        and~\ref{eq:SIRdes}. 
       %TODO equalize figure heights
        \begin{block}{}
          \begin{column}{.39\textwidth}
            \begin{figure}[h]
              \begin{center}
                \begin{tikzpicture}
                  \node [compartment] (S) {Susceptible (S)};
                  \node [compartment, below of=S] (I) {Infected (I)};
                  \node [compartment, below of=I] (R) {Recovered (R)};
                  \path [line] (S) -- node [compartment rate] {$\beta S(t)I(t)$} (I);
                  \path [line] (I) -- node [compartment rate] {$\gamma I(t)$} (R);
                \end{tikzpicture}
              \end{center}
              \caption{This flowchart depicts the standard SIR epidemiological
                       model. It is accomponanied by the system of differential
                       equations~\ref{eq:SIRdes}.}
              \label{fig:SIRFlowchart}
            \end{figure}
          \end{column}
          \begin{column}{.39\textwidth}
            \begin{figure}[h]
              \begin{align*}
                \frac{dS}{dt} &= -\beta S(t)I(t) \\
                \frac{dI}{dt} &= \beta S(t)I(t) - \gamma I(t) \\
                \frac{dR}{dt} &= \gamma I(t)\\
                N             &= S(t) + I(t) + R(t)\\
              \end{align*}
              \caption{The system of differential equations governing the SIR
                       model.}
              \label{eq:SIRdes}
            \end{figure}
          \end{column}
        \end{block}
      \end{block}

@@

      \vspace{-1.5em}

@@

        \begin{itemize}

@@

        \end{itemize}

@@

            \begin{description}
              \item[Active TB:]\hfill \\ 
                \$14,014.90
              \item[LTBI:]\hfill \\ 
                \$403.45
            \end{description}

@@

      \vspace{-.5em}

@@

        Agent based models capture disease dynamics on the individual level, and
        reflect stochasticity and granularity lost in compartmental models.
        Agent based counterparts to the Hill model were implemented in Netlogo
        and \texttt{c++}.

@@

      \begin{block}{Stochastic Models as a Measure of Variability}
        The stochastic model provides data on the variability of the results
        of the deterministic model.
        \begin{block}{}
          \begin{column}{.45\textwidth}
            \begin{figure}[h]
              \begin{center}
                \includegraphics[width=\textwidth]{IN0dist}
              \end{center}
              \caption{Distribution of USB Incidence (C++) with fitted Normal curve}
              \label{fig:IN0dist}
            \end{figure}
          \end{column}
          \begin{column}{.45\textwidth}
            \begin{figure}[h]
              \begin{center}
                \includegraphics[width=\textwidth]{IN1dist}
              \end{center}
              \caption{Distribution of FB Incidence (C++) with fitted Normal curve}
              \label{fig:IN1dist}
            \end{figure}
          \end{column}
        \end{block}
      \end{block}

      \begin{block}{Future Extensions}
        \begin{itemize}
          \item Including contact structure
          \item Multi-drug resistant TB
          \item HIV
        \end{itemize}
      \end{block}
